Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-09 paper.tex
Add citation for another verification study
Explain length of simulations

Time step dependence was evaluated using the 2-D $N_x=70$ grid, the results from
which are shown in Figure~\ref{fig:2d-br-verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum
at $\Delta t = 0.002$ s, with some divergence for smaller time steps, the reason
for which is unknown. The local minimum was chosen as the final time step to run
the simulations. Note that the SST model's convergence behavior may be due to
its specific implementation in OpenFOAM, and not indicative of the nature of the
model equations. Verification studies for CFTs with this level of detail in the
literature are not common, though the final time step is comparable to others
\cite{Balduzzi2016}. Note that while in general there may be a coupling between
necessary spatial and temporal resolution, these values were arrived at
iteratively, i.e., the spatial dependence was varied with the chosen time step,
and vice versa, such that there was one independent variable for each parameter
sweep.

@@

Turbine operation in all cases was simulated for 10 seconds, or approximately
six rotor revolutions. Computations for the 3-D cases were run on 192 processes
(24 nodes $\times$ 8 cores each on Sandia National Labs' Red Mesa high
performance computing cluster) and took on the order of 1,000 CPU hours per
second of simulated time. The 2-D simulations were run on a single processor and
took on the order of one CPU hour per simulated second.

>>>>

Time step dependence was evaluated using the 2-D $N_x=70$ grid, the results from
which are shown in Figure~\ref{fig:2d-br-verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum
at $\Delta t = 0.002$ s, with some divergence for smaller time steps, the reason
for which is unknown. The local minimum was chosen as the final time step to run
the simulations. Note that the SST model's convergence behavior may be due to
its specific implementation in OpenFOAM, and not indicative of the nature of the
model equations. Note that while in general there may be a coupling between
necessary spatial and temporal resolution, these values were arrived at
iteratively, i.e., the spatial dependence was varied with the chosen time step,
and vice versa, such that there was one independent variable for each parameter
sweep. Reassuringly, the chosen time step and average $y^+$ adjacent to the
blades are comparable to others reported in the literature
\cite{Maitre2013,Balduzzi2016}.

@@

Turbine operation in all cases was simulated for 10 seconds, or approximately
six rotor revolutions, to allow the revolution-averaged performance coefficient
to converge to within $\sim 1$ percentage point. Computations for the 3-D cases
were run on 192 processes (24 nodes $\times$ 8 cores each on Sandia National
Labs' Red Mesa high performance computing cluster) and took on the order of
1,000 CPU hours per second of simulated time. The 2-D simulations were run on a
single processor and took on the order of one CPU hour per simulated second.
